### 2022-09-29 main/frontmatter.tex
begin acknowledgements and other forematter tweaks

\begin{declaration}
\noindent
This dissertation is the result of my own work, except where explicit
reference is made to the work of others, and has not been submitted
for another qualification to this or any other university.
This dissertation does not exceed the word limit for the respective
Degree Committee.
\vspace*{1cm}
\begin{flushright}
Rupert~Tombs
\end{flushright}
\end{declaration}

\begin{acknowledgements}
<3
% Holly
% Dan
% Chris

% Friends who have come and gone from Homerton over the years

% Sarah Williams
% Ben Hooberman
% Jon Long

% Family, alive and dead.

This document uses parts of the ``hepthesis'' class~\cite{hepthesis}.
\end{acknowledgements}

>>>>

\begin{singlespacing}
\begin{declaration}
\noindent
\TODO{
This dissertation is the result of my own work, except where explicit
reference is made to the work of others, and has not been submitted
for another qualification to this or any other university.
This dissertation does not exceed the word limit for the respective
Degree Committee.
}
\vspace*{1cm}
\begin{flushright}
Rupert~Tombs
\end{flushright}
\end{declaration}
\end{singlespacing}

\begin{acknowledgements}
Warning: many thank-yous incoming.
Thank you, thank you, thank you, thank you
to all the friends and family who have come and gone during this project;
I feel much love for you all <3.

From the era of optimal office 958:
thank you to Daniel~Noel for the years of comradery, surviving this with me
--- I hope you enjoyed crushing me over the board;
thank you to Holly~Pacey and not only for antics with the non-sofa ---
you are an inspirational human and academic and I owe you endless thanks for
putting up with the ravings of my most miserable months on this
project\ldots\ oops!

\TODO{supervision}
% Sarah Williams
% for the opportunity to teach at Queens' and valuable experience from
% Christopher Gorham lester

\TODO{analysis team despite our time differences}

\TODO{Cantab}
% Tom Gillam
% Faridka Mustafazade
% Fred Desobry

\TODO{Cambridge: Tina, Richard, working group formerly known as SUSY}

For reviewing drafts of this thesis:
thank you to
Christopher Gorham Lester,
Holly Pacey, and
Daniel No\"el.
Your comments all had stunningly sharp precision and positive impacts on this
thesis and on my morale.

The Science and Technology Facilities Research Council supported this project.
This thesis template uses parts of the \textsc{hepthesis}
class~\cite{hepthesis}.
\end{acknowledgements}
